Rotation and Lithium Confirmation of a 500 Parsec Halo for the Open Cluster NGC\,2516\footnote{This is paper 3 of the Cluster Difference Imaging Photometric Survey.}

### 2021-04-23 cluster_paper/maintable_header.tex
update ms

%% Over-ride the default font size
%% Use Default (12pt)
\tabletypesize{\scriptsize}
%\tabletypesize{\small}

@@

@@

             \texttt{ref\_epoch} &              2015.5 &                                         Reference epoch for RA/dec. \\

@@

@@

         \texttt{is\_astrm\_bin} &                True &                                                 True if RUWE > 1.2. \\

>>>>

%% Over-ride the default font size
%% Use Default (12pt)
%\tabletypesize{\scriptsize}
\tabletypesize{\small}

@@

         \texttt{source\_id\_edr3} & 5290824530952816896 &                                                   Gaia EDR3 source identifier. \\

@@

@@

               \texttt{ref\_epoch} &              2015.5 &                           Reference epoch for right ascension and declination. \\

@@

           \texttt{is\_astrm\_bin} &                True &                                                  True if Gaia EDR3 RUWE > 1.2. \\
                     \texttt{ruwe} &            2.221799 &                                                                Gaia EDR3 RUWE. \\
      \texttt{Li\_EW\_mA\_GaiaESO} &                 NaN &                                    Gaia-ESO Li doublet equivalent width [m\AA] \\
\texttt{Li\_EW\_mA\_perr\_GaiaESO} &                 NaN & Gaia-ESO Li doublet EW 84$^{\mathrm{th}}$-50$^{\mathrm{th}}$ percentile [m\AA] \\
\texttt{Li\_EW\_mA\_merr\_GaiaESO} &                 NaN & Gaia-ESO Li doublet EW 50$^{\mathrm{th}}$-16$^{\mathrm{th}}$ percentile [m\AA] \\
        \texttt{Li\_EW\_mA\_GALAH} &                 NaN &                                       GALAH Li doublet equivalent width [m\AA] \\
  \texttt{Li\_EW\_mA\_perr\_GALAH} &                 NaN &    GALAH Li doublet EW 84$^{\mathrm{th}}$-50$^{\mathrm{th}}$ percentile [m\AA] \\
  \texttt{Li\_EW\_mA\_merr\_GALAH} &                 NaN &    GALAH Li doublet EW 50$^{\mathrm{th}}$-16$^{\mathrm{th}}$ percentile [m\AA] \\
